Verifying Demonstrations

### 2018-02-28 paper/intro.tex
update of properties.tex

%Seb: I suggest that we move this part to system model
%\subsection{Combining properties of electronic voting with location proofs}
\emph{Relationship between protesting and electronic voting}. In general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal the individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can 
    be used as a proof of how the voter voted.
  \item[Coercion pesistance:] a voter cannot cooperate with a coercer to prove 
    the vote was cast in any particular way.
\end{description}
We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not

@@

In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}
%Seb: above, we should put the reference to the Schnorr protocol 
In addition, this allows us to form distance-bounding anonymous credentials.

>>>>

@@

In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
%Seb: above, we should put the reference to the Schnorr protocol 
In addition, this allows us to form distance-bounding anonymous credentials.

### 2018-02-28 paper/properties.tex
typo
update of properties.tex

\section{Desired security properties}%
\label{Properties}

@@

We have three \emph{malicious} adversaries: Alice, Grace and Mallory.
Alice the activist (and all the protesters) try to increase the count.
Grace the totalitarian dictator tries to decrease the count.
Additionally, Grace tries to deanonymize the participants to arrest them or 
\emph{convince} them to change their minds.
Finally, we have Mallory who is represents another nation state.
Mallory has some interest in affecting the state of Grace's regime, for Mallory's own 
gain, thus supporting either Grace or Alice as he see fits.
Mallory will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

@@

We desire three verifiability requirements:

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedGracent} prove that the data is designated for the event.
    \end{requirements}

  \item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
    result is according to the submitted participation proofs.
  \item\label{IndividualVerif} Individual verifiability: every participant can 
    verify that their participation proof is included in the global count.
\end{requirements}
We will now discuss these in more detail.

\subsubsection{Temporal eligibility}

@@

We also need privacy in addition to the verification requirements.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
and Bob by the data.
So as long as Alice and Bob can conceal their identities at the demonstration 
and escape without arrest, their support is recorded in the data while their 
privacy is not violated.
(Following this line of thinking, it can actually be beneficial for the privacy 
of the demonstrators to mix with the participants of any counter-demonstrations 
--- since the counts will still be correct.)

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
\eg Grace can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

>>>>

\section{Security requirements}%
\label{Properties}

@@

On our setting, we have three potential adversaries: Alice, Eve and Mallory.
%Seb: I changed the name of Grace to Eve to be consistent with the introduction
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
gain, thus supporting either Eve or Alice as he see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
%Seb: we have to justify why Mallory is not captured either by Alice or Eve
In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.

Note that in general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting. 
To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.

@@

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that it has not been counted before.
    \begin{requirements}
    \item \emph{Temporal eligibility}:%
      \label{CreatedAfterStart} prove that the proof was created after the start of the protest and
      %\label{CreatedBeforeEnd} prove that the proof was created 
      before the end of the protest.
    \item \emph{Spatial eligibility}
      \label{SpatiallyRelated} prove that the proof is spatially related to the physical location or journey of the protest.
    \item \emph{One-proof-per-person}:%
      \label{CountOnce} prove that no individual can be counted more than once for a particular protest.
    \item \emph{Designated event}:%
      \label{DesignatedEvent} prove that the proof is designated for the protest.
    \end{requirements}

  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that their participation proof is included in the global count.
\end{requirements}

We will now discuss these properties in more details focusing in particular to the one related specifically to the protest.

%Seb: to complete
\subsubsection{Temporal eligibility}

@@

In addition to the verification requirements, we also need to formalize the privacy properties.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
%Seb: I think this sentence should be clarified
(Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)

In voting protocols, there are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{requirements}[P]
\item\label{VotePrivacy} \emph{Vote privacy}: the voting does not reveal any individual vote.
\item\label{ReceiptFreeness} \emph{Receipt freeness}: the voting system does not provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} \emph{Coercion resistance}: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
\end{requirements}

\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that \cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies \cref{VotePrivacy}. 
\Cref{CoercionResistance} is probably not possible to achieve for protests:
\eg Grace can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not
